---
title: "Analiza Przeżycia"
subtitle: "Raport 2"
author: "Filip Michewicz 282239  \n  Wiktor Niedźwiedzki 258882"
date: "23 listpada 2025 Anno Domini"
output:
  pdf_document:
    number_sections: true
toc: true
lof: true
lot: true
header-includes:
  - \usepackage[OT4]{polski}
  - \usepackage[utf8]{inputenc}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \renewcommand{\contentsname}{Spis treści}
  - \renewcommand{\listfigurename}{Spis wykresów}
  - \renewcommand{\listtablename}{Spis tabel}
  - \renewcommand{\figurename}{Wykres}
  - \renewcommand{\tablename}{Tabela}
  - \usepackage{xcolor}
  - \definecolor{ForestGreen}{rgb}{0.1333, 0.5451, 0.1333}
  - \definecolor{SteelBlue}{rgb}{0.2745, 0.5098, 0.7059}
  - \definecolor{Tomato}{rgb}{1.0, 0.3882, 0.2784}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  dpi = 1200,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  eval = TRUE,
  echo = FALSE,
  fig.align="center",
  fig.width = 7,
  fig.height = 5,
  fig.pos = "H",
  out.extra = '')
```

```{r biblioteki+zmienne_pomocnicze}
library(knitr)
library(latex2exp)
library(xtable)
library(ggplot2)
library(survminer)

set.seed(21370)
```


\newpage
# Lista 5

## Zadanie 1

### Estymator Kaplana-Meiera

### Estymator Fleminga-Harringtona

## Zadanie 2

## Zadanie 3

### Estymacja wartości funkcji przeżycia w punktach $t_0$ oraz $2 t_0$ 

### Histogramy oszacowań $t_0$ oraz $2 t_0$ 

\newpage
# Lista 6

## Zadanie 1

### Estymator Kaplana-Meiera

### Estymator Fleminga-Harringtona

## Zadanie 2

\newpage
# Lista 7

## Zadanie 1

## Zadanie 2

\newpage
# lista 8

## Zadanie 1

## Zadanie 2

\newpage
# Zadania dodatkowe

## Zadanie 1

## Zadanie 2

## Zadanie 3
